Scaffolder - Software for \change{Reproducible}{Manual} Genome Scaffolding.

### 2011-08-14 src/article.tex
Revise implementation section

Scaffolder is written in the Ruby programming language using version 1.8.7
\cite{ruby-lang}. The scaffolder package is split into two libraries. The
first called ``scaffolder'' provides the core Scaffolder application
programming interface (API). The second library ``scaffolder-tools'' provides
the Scaffolder command line interface (CLI). \pb

@@

The scaffolder algorithm reads through the scaffolder file parsing. Each entry
is then converted to corresponding nucleotide sequence by fetching from the
FASTA file and then performing any designated sequence trimming or reverse
complementing. Each of the sequence entries are then joined into a continuous
single super-sequence and returned to the console output. \pb

>>>>

Scaffolder is written in the Ruby programming language \change{using version
1.8.7}{and tested against versions 1.8.7 and 1.9.2} \cite{ruby-lang}. The
scaffolder package is split into two libraries. The first called ``scaffolder''
which provides the core Scaffolder application programming interface (API). The
second library ``scaffolder-tools'' provides the Scaffolder command line
interface (CLI). \pb

@@

\remove{The scaffolder algorithm reads through the scaffolder file parsing.
Each entry is then converted to corresponding nucleotide sequence by fetching
from the FASTA file and then performing any designated sequence trimming or
reverse complementing. Each of the sequence entries are then joined into
a continuous single super-sequence and returned to the console output.}
